### 2017-12-11 Maths Notes/D2/Transportation problems/Transportation problems.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{enumerate}

@@

\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&&\cblue{$14$}&&&14\\
\hline
B&\cblue{$11$}&\cblue{$1$}&\cblue{4}&&16\\
\hline
C&&&\cblue{10}&\cblue{10}&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
The cost of this is £7580, a reduction from the initial solution.\\
\textbf{AW has become empty, meaning it is the exiting cell}\\
\textbf{To find an optimal solution, new shadow costs and improvement indices would need to be found}

>>>>

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{enumerate}
\usetikzlibrary{calc,shapes.geometric, arrows}
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30,text width=2cm]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&&\cblue{$14$}&&&14\\
\hline
B&\cblue{$11$}&\cblue{$1$}&\cblue{4}&&16\\
\hline
C&&&\cblue{10}&\cblue{10}&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
The cost of this is £7580, a reduction from the initial solution.\\
\textbf{AW has become empty, meaning it is the exiting cell}\\
\textbf{To find an optimal solution, new shadow costs and improvement indices would need to be found}
\newpage
\section{Finding an initial solution to the transportation problem}
\begin{tikzpicture}[node distance=2cm]
\node (start) [startstop] {Start};
\node (pro1) [process, below of=start] {Allocate NW Corner};
\node (dec1) [decision, below of=pro1, yshift=-2cm] {Is all stock exhausted and all demand met?};
\node (dec2) [decision, below of=dec1, yshift=-3cm] {Stock Empty?};

\node (pro2) [process, below of=dec2,yshift=-1cm] {Down 1};
\node (pro3) [process, right of=dec2,xshift=3cm] {Right 1 and Allocate};

\node (dec3) [decision, below of=pro2, yshift=-1cm] {Demand Satistied?};
\node (pro4) [process, right of=dec3,xshift=3cm] {Allocate};
\node (pro5) [process, right of=dec3,xshift=3cm,yshift=-4cm] {Right 1 and Allocate};
\node (stop) [startstop,left of=dec1,xshift=-3cm] {Stop};

\draw [arrow] (start) -- (pro1);
\draw [arrow] (pro1) -- (dec1);
\draw [arrow] (pro2) -- (dec3);
\draw [arrow] (dec1) -- node[anchor=south] {Yes} (stop);
\draw [arrow] (dec1) -- node[anchor=east] {No} (dec2);
\draw [arrow] (dec2) -- node[anchor=east] {Yes} (pro2);
\draw [arrow] (dec2) -- node[anchor=south] {No} (pro3);

\draw [arrow] (dec3) |- node[anchor=east,yshift=2cm] {Yes} (pro5);
\draw [arrow] (dec3) -- node[anchor=south] {No} (pro4);
\draw [arrow] (pro5.east) --  (9,-21)-- (9,-3.79)-- (dec1.north);
\draw [arrow] (pro3.east) -- (9,-11);
\draw [arrow] (pro4.east) -- (9,-17);
\end{tikzpicture}
\newpage
\section{Finding an improvement to the initial solution}
